NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-10-06 main.tex
Update figures and text

\begin{figure}[tb]
    \centering
    \includegraphics[width=180mm]{Figures/permeation2.pdf}
    \caption{A 
    {\bf B-E} Water permeation through membranes analyzed from the databank as a function of temperature, thickness, area per lipid, and acyl chain order. Values from simulations with non-zero permeation values are shown with blue dots. Averages over fixed range of x-axis values are shown with black dots. Insert in B) shows the Arrhenius plot of permeation ($\ln$ (P) vs. 1/T) that gives 17\,$\pm$\,4\,k$_b$T for the average activation energy for water permeation through lipid bilayer. Inserts in C) and D) show the region where the dependence could be considered approximately linear.
    {\bf F-G} Diffusion anistoropy of water as a function of thickness and area per lipid.
    {\bf H} Lateral diffusion of water as a function of hydration level. Experimental points for DMPC bilayers at 313\,K at different hydration levels are shown~\cite{rudakova04}.}
    \label{fig:permeability}
\end{figure}

To analyze the anisotropic diffusion of water in membrane environment, we also calculated the water translational diffusion along the membrane surface from all simulations in the NMRlipids databank. The results at different hydration levels are shown in Fig.~\ref{fig:permeability} H together with the experimental data~\cite{rudakova04}. 
%The experimental water diffusion increases with increasing hydration level toward the value for bulk water . 
%As expected, water translational diffusion increase in the diffusion is observed with the increased temperature and hydration level (Figs.~\ref{fig:permeability} H and~\ref{fig:diffusionSI} B). 
Simulation results are close to the experimental values at low hydration levels, but increase to the values of approximately two times higher than experimental bulk water diffusion value (3.1$\cdot$\,10$^{-9}$\,m$^2$/s at 313\,K~\cite{khakimov08}) at high hydration levels. 
This is not surprising as the most common water model used in membrane simulations, TIP3P, overestimates the bulk water diffusion~\cite{??}. The water translational diffusion incereased with the temperature, but dependencies on membrane area per lipid, thickness, or fraction of charged lipids were not observed in Fig.~\ref{fig:diffusionSI} in the supplementary information. In order to estimate the diffusion anistoropy of water in multilamellar membrane system, we translated the water permeation coefficients through membranes to diffusion coefficients through multilamellar stack using the Tanner equation~\cite{??}. The resulting diffusion coefficients through the membranes are approximately five orders of magnitude slower than along the membrane (Figs.~\ref{fig:permeability} F and G), which is at the upper limits of the anisotropic estimated from the experimental data~\cite{nitsche19}. Relatively high anisotropy is understandable as simulations give slightly slower permeation rates and higher lateral diffusion rates than experiments. Significant increase in the diffusion anisotropy with membrane packing is observed, as $D_{\perp}/D_{||}$ drifts away from one with decreasing area per lipid and increasing thickness in Figs.~\ref{fig:permeability} F and G.
This follows from decreasing water permeability with membrane packing (Figs \ref{fig:permeability} C and D), while lateral diffusion remains approximately constant (Fig. \ref{fig:diffusionSI} A and C).

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=180mm]{Figures/permeation2.pdf}
    \caption{A 
    {\bf B-E} Water permeation through membranes analyzed from the databank as a function of temperature, thickness, area per lipid, and acyl chain order. Values from simulations with non-zero permeation values are shown with blue dots. Averages over fixed range of x-axis values are shown with black dots. Insert in B) shows the Arrhenius plot of permeation ($\ln$ (P) vs. 1/T) that gives 17\,$\pm$\,4\,k$_b$T for the average activation energy for water permeation through lipid bilayer. Inserts in C) and D) show the region where the dependence could be considered approximately linear.
    {\bf F} Lateral diffusion of water as a function of hydration level. Experimental points for DMPC bilayers at 313\,K at different hydration levels are shown~\cite{rudakova04}.
    {\bf G-H} Diffusion anistoropy of water as a function of thickness and area per lipid. }
    \label{fig:permeability}
\end{figure}

To analyze the anisotropic diffusion of water in membrane environment, we also calculated the water translational diffusion along the membrane surface from all simulations in the NMRlipids databank. The results at different hydration levels are shown in Fig.~\ref{fig:permeability} F together with the experimental data~\cite{rudakova04}. 
%The experimental water diffusion increases with increasing hydration level toward the value for bulk water . 
%As expected, water translational diffusion increase in the diffusion is observed with the increased temperature and hydration level (Figs.~\ref{fig:permeability} H and~\ref{fig:diffusionSI} B). 
Simulation results are close to the experimental values at low hydration levels, but increase to the values of approximately two times higher than experimental bulk water diffusion value (3.1$\cdot$\,10$^{-9}$\,m$^2$/s at 313\,K~\cite{khakimov08}) at high hydration levels. 
This is not surprising as the most common water model used in membrane simulations, TIP3P, overestimates the bulk water diffusion~\cite{??}. The water translational diffusion incereased with the temperature, but dependencies on membrane area per lipid, thickness, or fraction of charged lipids were not observed in Fig.~\ref{fig:diffusionSI} in the supplementary information. In order to estimate the diffusion anistoropy of water in multilamellar membrane system, we translated the water permeation coefficients through membranes to diffusion coefficients through multilamellar stack using the Tanner equation~\cite{??}. The resulting diffusion coefficients through the membranes are approximately five orders of magnitude slower than along the membrane (Figs.~\ref{fig:permeability} G and H), which is at the upper limits of the anisotropic estimated from the experimental data~\cite{nitsche19}. Relatively high anisotropy is understandable as simulations give slightly slower permeation rates and higher lateral diffusion rates than experiments. Significant increase in the diffusion anisotropy with membrane packing is observed, as $D_{\perp}/D_{||}$ drifts away from one with decreasing area per lipid and increasing thickness in Figs.~\ref{fig:permeability} G and H.
This follows from decreasing water permeability with membrane packing (Figs \ref{fig:permeability} C and D), while lateral diffusion remains approximately constant (Fig. \ref{fig:diffusionSI} A and C).
